Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-17 ms.tex
clean up

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}
\newcommand{\FIRAS}{{\it FIRAS}}

@@

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. \IRAS, with its $\sim$4$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using 60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Then, beginning in 1989, DIRBE provided
complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. COBE/\FIRAS~\citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 
narrow frequency bins between 200 GHz and 2100 GHz.

\cite{FDS99} (hereafter FDS99) used \FIRAS~data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that a model consisting of a single MBB with power law index 
$\beta$ 
could not accurately match the \IRAS/\FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 proposed
a dust emission model consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
amorphous silicates and carbonaceous grains.

>>>>

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}
\newcommand{\COBE}{{\it COBE}}

@@

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
frequency bins between 200 GHz and 2100 GHz.

\cite{FDS99} (hereafter FDS99) used FIRAS data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that a model consisting of a single MBB with power law index 
$\beta$ could not accurately match the \IRAS/FIRAS/DIRBE spectrum at both the 
Wien and Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 
proposed a dust emission model consisting of two MBBs, each with a different
temperature and power law index. Physically, these two components
represent distinct dust grain species within the ISM, specifically 
amorphous silicates and carbonaceous grains.
